Social Computing Article\thanks{This title is temporary}

### 2013-01-24 Article.tex
Incluí as modificações que o Lamb e o Diego sugeriram
Alguns comentários eu deixei como... comentários. Pra depois a gente
passar pelo texto e ver como arrumar.

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in a diverse set of environments. Nevertheless, if not well designed, a social human computation system may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

For years multi-agent systems have been used to research cooperation as a tool for problem-solving. Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents. Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}. However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour. In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment. The control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the ones displayed by humans.

Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition. However, it would be useful to be able to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive. The different sets of abilities between computers and humans suggest that the latter might provide a new approach to those problems that might be more effective than current techniques employed by computers. That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP). A software that presents the problem to humans as an online computer game, called \emph{Foldit}~\cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power. Those results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}. However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional techniques. To take full advantage of human problem-solving strategies, we must learn their limitations. In order to obtain that knowledge, our system simulates human behaviour according to findings of social computation experiments.

@@

Social computation is a relatively new area of research with a diversified, interdisciplinary root that mixes social sciences, artificial intelligence, game theory and network science, among others. Only recently studies on the potential of human social networks for solving problems are gaining some popularity. Those have provided insights into, among other things, the impact of network structure in the collaboration process and the factors that lead neighbours' proposed solutions to be copied by individuals.

The origin of human computation as we know it today can be traced back to the work of~\cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation. That is an idea that also appears in the Foldit game.

@@

Other initiatives have appeared, such as the ones by~\cite{farenzena:collabem} and~\cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours. Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers makes itself present. It's in those models of experiments that we will focus in this work.

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question. In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one. That behaviour is referred to as an evidence of conformism by the human subjects. On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that fact wasn't provided. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons for that in the \emph{Results} section.

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while still remaining NP-complete and equivalent to SAT. Through that process, we compared the behaviour observed in humans with other strategies and reached the conclusion that it is detrimental to the problem-solving process. We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy. In addition, we analyse the impact that copying and guessing have on the solving of the problem. After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.

\section{A Novel Method for Artificial Social Problem Solving}

@@

We propose a method for solving computational problems by the means of a network of agents with social behaviour. Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents. Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}.

\begin{algorithm}
 \SetAlgoLined
 Initialize N agents, each encoding a partial solution to the problem\;
 \While{termination condition not met}
 {
 	\For{i = 1 to N}
 	{
 		\For{j = 1 to N}
 		{
 			\If{j is connected to i}
 			{
 				$A_{i}$ = $i_{th}$ agent\;
 				$A_{j}$ = $j_{th}$ agent\;
 				Add $A_{j}$'s solution to the collection of messages of $A_{i}$\; %A.messages.add(j.solution)\;
 			}
 		}
 	}
 	\For{i = 1 to N} 
 	{
 		\CommentSty{ //Social Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		selectedMessage = select($A_{i}$.messages)\;

@@

\begin{itemize}
\item
Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections. Agents are thus presented with a multiplicity of messages. There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions. We call this probability the {\em Copy Rate}. When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages. This is done by the means of a particular message-selecting metric.

\item
Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by the means of a heuristic or an exact method.
\end{itemize}

\section{Performance Tests}

@@

\subsection{Social Stage}

@@

\subsubsection{{\em Pick Most Filled} metric}

@@

\subsubsection{{\em Pick Among First} metric}

@@

\subsubsection{{\em Pick Random} metric}

@@

{\em Sudoku} solving techniques are abundant in {\em Sudoku} strategy literature. Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles. Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.

@@

We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) had an equal representation in the population. We performed tests with varying values for the parameters of {\em copy rate}, {\em guess rate}, {\em message selecting metric} and {\em network topology}.

@@

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_prob}
\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob}
\end{figure}

@@

Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance. To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process. On the contrary, in several cases it actually contributes to advancing the solution. The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem individually without some guessing mechanism, and the high {\em copy rates} allow them to correct wrong guesses through copying better agents' solutions.

@@

We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given iteration, follows a normal distribution. During the first few iterations no agents have found the solution. Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem. From that point onwards the solution starts spreading through the network. As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}. That leads the number of agents to obtain the solution to progressively increase in the following iterations, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.

We have run experiments in the four different topologies enumerated above, for 7 different problem instances, and obtained similar results in each. The progression of the solution for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance. In the context of the experiments, the mean indicates how soon the correct solution was found, and the variance how long it took to spread through the network. The exact values for those parameters vary widely according to factors such as topology and problem instance, but they follow a particular pattern. For all cases, the strategy that evaluated solutions had lower mean, indicating the solution was found sooner, and lower variance, meaning it spread faster. We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively. In each can be seen the percentage of agents that find the correct solution in each iteration for the two strategies, with normal curves plotted over the values, evidencing the described behaviour. It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.

@@

Our experiments, however, have shown that although completeness is not necessarily an accurate measurement of quality, it was good enough to lead the network to the right solution. Not only that, it consistently performed better than the other strategies, even with high guess rates. That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail. Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation. Therefore, it is not necessary for the problem addressed to have an exact metric to compare different possible solutions. An imperfect metric is good enough to be employed in a problem-solving social network.

@@

\section{Conclusions and Further Work}

>>>>

\begin{abstract}
Social collaboration has been shown to facilitate problem-solving activity in diverse sets of environments. Nevertheless, if not well designed, social and human computation systems may achieve results as poor as those of a single human subject performing a task. This scenario reflects a need for a better understanding of the performance issues of human problem-solving social networks. We present a novel method for artificial social problem solving and test it against results with human subjects, analysing which parameters have effects on the performance of problem-solving social networks. Results show that evaluating neighbours' solutions in order to decide from which neighbour to copy or mimic is significantly better than selecting solutions based on their position on the graphic interface, as tests with human subjects have shown to be the preferred behaviour among people. Our results also indicate that copying and guessing are highly beneficial to the performance of these social networks. We then use these results to propose a collection of guidelines concerning the design of a efficient human computation system.
\end{abstract}

@@

For years multi-agent systems have been used to research cooperation as a tool for problem-solving. %cite Malone
Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents. Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}. However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed collective, human behaviour. In this paper, we use a multi-agent based simulation to complement %change?
the study of human computation, as a way of explaining the strategies used by humans when solving problems and understanding their consequences in a cooperative environment. The degree of control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the actions and behaviours displayed by human agents.

Human beings are known to be able to easily perform tasks which are still generally difficult for computers, such as natural language processing and image recognition.
%--
However, it would be useful to apply human social computation to more straightforward computer problems with precise definitions and algorithms, but which are still computationally intensive.
%--
The different abilities of computers and humans suggest that the latter might provide a new approach to problems that might be more effective than current techniques employed by computers. That notion has been successfully applied, for example, in one of the most significant problems in the field of bioinformatics: protein structure prediction (PSP). A software that presents the problem to humans as an online computer game, called \emph{Foldit}~\cite{cooper:foldit}, has produced significant results in the research of PSP, which is usually approached as an optimization problem requiring extensive computational power. Such results have been attributed to human visual problem-solving and decision-making abilities, as well as social collaboration~\cite{cooper:foldit}. However, we still don't know the limits of human abilities in problem-solving and how they compare to more traditional computational techniques.
%--Exploit this point
In order to take full advantage of human problem-solving strategies, we must learn their limitations. Humans tend to be less efficient than computers in mathematical computations, are subject to a series of physical and psychological conditions that might affect their performance, and do not always act rationally.
We propose a model for simulating a problem-solving network of human agents. By applying in this model findings of experiments performed in humans, we can obtain knowledge about how human patterns of behaviour influence the problem-solving process. Through this system, it becomes possible to draw new conclusions from past observations of human behaviour. The model can be used, for example, to preview the results that changes in the infrastructure of a social computation system will have on its performance before actually performing the experiments with humans. Another possibility is to use the results obtained by the simulation of past experiments to plan the best configuration for a new system of social computing.
%--Move to Contribution?

@@

Human and social computing are relatively new areas of research with a diversified, interdisciplinary root that mixes social sciences, artificial intelligence, game theory and network science, among others. %cite ?, Kleinberg
Only recently studies on the potential of human social networks for solving problems are gaining some popularity. %cite Malone, Kearns
Those have provided insights into, among other things, the impact of network structure in the collaboration process and the factors that lead neighbours' proposed solutions to be copied by individuals.

The origin of human computation as we know it today can be traced back to the work of~\cite{vonahm:gwap}, which identified the possibility of using entertainment as an incentive to participation of human subjects, applying it in games in which the participants are actually performing a computation. That is an idea that also appears in the Foldit game. %cite

@@

Other initiatives have appeared, such as the ones by~\cite{farenzena:collabem} and~\cite{mason:collablearnet}, which take a different approach by having subjects trying to solve the collective problem individually, with the possibility of exchanging solutions between neighbours. Those have resulted in interesting conclusions on human behaviour when the possibility of copying peers is available. Our experiments follow this line of research.

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question.
%--Make more specific
In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one.
%--
That behaviour is referred to as an evidence of conformism in human subjects. On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although %Unfortunately?
an in-depth analysis of that fact was not reported. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons for that in the \emph{Results} section. %We also analyse possible reasons for that behaviour in the \emph{Results} section.

@@

%--Keep?
We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}.
%--
It was then applied to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We limited our experiments to the {\em Sudoku} problem, which is more attractive and accessible to human beings while being NP-complete and equivalent to SAT. Through that process, we compared the problem-solving strategy %strategy?
typically used by humans with alternative, artificial strategies and reached the conclusion that it is detrimental to the problem-solving process.
%--Explain better
We verify that even an inaccurate metric of evaluation surpasses choosing an arbitrary neighbour to copy.
%--
In addition, we analyse the impact that copying and guessing have on the process of solving the problem. After obtaining those results, we are able to propose a set of guidelines for the design of social problem-solving systems that might address those issues and improve the performance of human computing.

\section{A Novel Method for %Artificial?
Social Problem Solving}
%P.S. method has two phases: communication and reasoning

@@

We propose a method for solving computational problems by means of a network of agents endowed with social behaviour. Our algorithm is composed of an ordered set of $N$ agents, each encoding a partial solution to the problem, and a binary $N \times N$ matrix representing possible connections between agents. Additionally, our algorithm is composed of two stages, namely the {\em Social Stage} and the {\em Cognitive Stage}. %cite social psych

\begin{algorithm}
 \SetAlgoLined
 Initialize N agents, each encoding a partial solution to the problem\;
 \While{termination condition not met}
 {
 	\For{i = 1 to N}
 	{
 		\For{j = 1 to N}
 		{
 			\If{j is connected to i}
 			{
 				$A_{i}$ = $i_{th}$ agent\;
 				$A_{j}$ = $j_{th}$ agent\;
 				Add $A_{j}$'s solution to the collection of messages received by $A_{i}$\; %A.messages.add(j.solution)\;
 			}
 		}
 	}
 	\For{i = 1 to N} 
 	{
 		\CommentSty{ //Social Stage }\;
 		$A_{i}$ = $i_{th}$ agent\;
 		selectedMessage = select($A_{i}$.messages)\;

@@

\begin{itemize}
\item
Social Stage: In the {\em Social Stage}, messages are passed from agent to agent through the network connections. Agents are thus presented with a multiplicity of messages. There is a particular probability associated with the behaviour of agents choosing to copy one of these solutions in contrast to keeping their current solutions. We call this probability the {\em Copy Rate}. When an agent chooses to copy, he or she is then supposed to select for copying only one of his or her received messages. This is done by means of a particular message-selecting strategy.

\item
Cognitive Stage: In the {\em Cognitive Stage}, agents are supposed to add local changes to the messages copied in the previous stage. This is done by means of a heuristic or an exact method.
\end{itemize}

%--Change focus
\section{Performance Tests}
%--

@@

\subsection{Social Stage} %Generalize!

@@

\subsubsection{{\em Pick Most Filled} strategy}

@@

\subsubsection{{\em Pick Among First} strategy}

@@

\subsubsection{{\em Pick Random} strategy}

@@

{\em Sudoku} solving techniques are abundant in literature. %{\em Sudoku} strategy literature?
Those techniques are based on the reasoning usually employed by humans to solve \emph{Sudoku} puzzles. Davis~\cite{davis:mathsudoku} discusses a collection of these techniques, of which the {\em Naked Singles} rule, the {\em Hidden Singles} rule and the {\em Naked Twins} rule are some examples. These techniques intend to, given a partial {\em Sudoku} solution, generate a set of {\em movements} which can be used to mark cells of this {\em Sudoku} puzzle. We implemented $5$ of these rules, modelling each one of them as a function that maps a {\em Sudoku} partial solution to a set of {\em movements}. These functions can be used in the {\em Cognitive Stage} to add local changes to the {\em Sudoku} message received in the {\em Social Stage}.

@@

We tested the above modelling using an heterogeneous, uniform agent distribution in which every agent {\em level} ($0$ to $5$) %explain; table?
had an equal representation in the population. We performed tests with varying values for the parameters of {\em copy rate}, {\em guess rate}, {\em message selecting metric} and {\em network topology}.

@@

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_prob}
\caption{Effects of copy rate and guess rate on the collective's problem solving performance (scale-free topology with 'pick among first' selection metric)
}
\label{fig:copy_guess_free_prob}
\end{figure}

@@

Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance. To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process. On the contrary, in several cases it actually contributes to advancing the solution. The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer rounds are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the problem, not knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem individually without some guessing mechanism, and the high {\em copy rates} allow them to correct wrong guesses through copying better agents' solutions.

@@

We have observed in our experiments that the progress of the solution, represented by the number of agents that solve the problem in a given round, follows a normal distribution. During the first few rounds no agents have found the solution. Then, in a moment that varies according to the particular instance of the problem, the first few agents solve the problem. From that point onwards the solution starts spreading through the network. As more agents obtain the complete solution, more likely it becomes that further agents will copy that solution from their neighbours, according to the conformist behaviour observed in~\cite{farenzena:collabem}. That leads the number of agents to obtain the solution to progressively increase in the following rounds, until it reaches a point where the few remaining agents take longer to obtain the solution due to factors such as being less capable solvers or being in unfavourable positions in the topology.

We have run experiments in the four different topologies enumerated above, for 7 different problem instances, and obtained similar results in each. The progression of the solution for the \emph{Most Filled} and \emph{First Positions} strategies can be described as normal distributions of different mean and variance. In the context of the experiments, the mean indicates how soon the correct solution was found, and the variance how long it took to spread through the network. The exact values for those parameters vary widely according to factors such as topology and problem instance, but they follow a particular pattern. For all cases, the strategy that evaluated solutions had lower mean, indicating the solution was found sooner, and lower variance, meaning it spread faster. We have chosen the scale-free and 3-ring topologies as representative examples, and plotted the average of the results for a same instance of the problem for each in Figures~\ref{fig:sf_gauss} and~\ref{fig:ring_gauss}, respectively. In each can be seen the percentage of agents that find the correct solution in each round for the two strategies, with normal curves plotted over the values, evidencing the described behaviour. It's noticeable that the results fluctuate more for the second strategy, which is explained by its practically random method of choosing solutions to copy.

@@

Our experiments, however, have shown that although completeness is not necessarily an accurate measurement of quality, it was good enough to lead the network to the right solution. Not only that, it consistently performed better than the other strategies, even with high guess rates.
%--Explain
That means that the incorrect guesses were successfully filtered out, allowing the correct solutions to prevail.
%--
Those results might extend to other constraint satisfaction problems that don't have an accurate method of evaluation. Therefore, it is not necessary for the problem addressed to have an exact metric to compare different possible solutions. An imperfect metric is good enough to be employed in a problem-solving social network.

@@

\section{Conclusions and Further Work}
%"An interesting, unexpected result... (filtered)"
%Swap first two sentences
